---
title: "lab4-vignette"
output: rmarkdown::html_vignette
author: Dharani Ganesan and Marc Braun
vignette: >
  %\VignetteIndexEntry{lab4-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab4)
```

## Setup
To install the lab4 package, source it from GitHub with the command `devtools::install_github("Marbr987/lab4")`.

## Usage of linreg function
The `linreg()` function can be used to perform a linear regression. It takes two arguments, `formula` and `data`, where `formula` is the formula consisting of parameters of `data` used to perform the regression. The function returns an object of class linreg.  
The following example illustrates the use of `linreg()` with the `iris` dataset, which is also included in this package.

```{r}
# Crate an object of class linreg by calling the linreg function
linreg_obj <- linreg(formula = Petal.Length ~ Species, data = iris)
class(linreg_obj)

# The linreg object is a list containing the following elements
names(linreg_obj)
```

## Usage of methods for linreg objects
The `print()` method prints out the call of the function and the coefficients of the linear regresion.
```{r}
print(linreg_obj)
```

The `plot()` function provides the two plots shown in the example below. It returns the plots in a list of size two.
```{r, fig.width=7, fig.height=6}
plot_list <- plot(linreg_obj)
print(plot_list[1])
print(plot_list[2])
```

The `resid()` method prints out the residuals of the linear regression.
```{r}
head(resid(linreg_obj))
```

The `pred()` method prints out the target values predicted by the linear regression.
```{r}
head(pred(linreg_obj))
```

The `coef()` method prints out the coefficients of the linear regression.
```{r}
coef(linreg_obj)
```

The `summary()` method prints a summary of the linear regression as seen in the example below.
```{r}
summary(linreg_obj)
```



